Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-23 Final/Final20181223.Rmd
.

In order to see how products, which is exported to Turkey, cluster, we implemented k-means clustering method after scaling the values

@@

```{r, fig.align="center"}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

@@

#Determine optimal cluster with Elbow Method
set.seed(11)
Elbow <- fviz_nbclust(product_Cluster2, kmeans, method = "wss")

@@

@@

fviz_cluster(k3, data = product_Cluster2) + ggtitle("k = 4")

@@

@@

>>>>

In order to see the segmentation of exported products by Turkey considering their share in total export value, we implemented k-means clustering method after scaling the export values of each product.

@@

```{r, fig.align="center", fig.height=5 , fig.width=8}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

@@

```{r, fig.align="center", fig.height=4 , fig.width=10}
#Determine optimal cluster with Elbow Method
set.seed(11)
Elbow <- fviz_nbclust(product_Cluster2, kmeans, method = "wss")

@@

```{r, fig.align="center", fig.height=7 , fig.width=10}

@@

@@

```{r, fig.align="center", fig.height=8 , fig.width=15}
fviz_cluster(k3, data = product_Cluster2) + ggtitle("k = 4")
```

@@

[r-statistics.co](http://r-statistics.co/)
